Towards Practical First-Order Model Counting

### 2024-01-04 paper.tex
Describe some changes to the compilation process

An important change to the compilation algorithm. We make the FCGs satisfy the
following property. For every domain $\Delta$, for every directed path $P$
without Ref nodes, the number of atom counting or (generalised) domain recursion
operations on $\Delta$ on $P$ is at most one.

>>>>

% TODO: (in Fig. 1) Crane2 doesn't use Crane, it uses itself.

\paragraph{Changes to the compilation process.}
\begin{itemize}
  \item We make the FCGs satisfy the following property. For every domain
        $\Delta$, for every directed path $P$ without Ref nodes, the number of
        atom counting or (generalised) domain recursion or independent partial
        grounding operations on $\Delta$ on $P$ is at most one.
  \item when checking whether recursion is possible between a source and a
        target formula, the target formula (maybe the source formula as well?)
        must not include a domain as well as its subdomain. This might be
        equivalent to the formula being `unshattered'. Such formulas could be
        seen as transitory, and allowing such recursive calls leads to FCGs that
        I cannot make sense of.
  \item During smoothing, when unit clauses (a.k.a.\ variables) are propagated
        in the opposite direction of the FCG arcs (i.e., `upwards'), when
        visiting a \texttt{Ref} node, these clauses are translated using the
        domain map of the \texttt{Ref} node. For example, we might have a
        function $g$ that depends on $m$ (i.e., domain $a^{\top}$), which is
        called as $g(n)$ (i.e., on domain $a$). When smoothing that function
        call, we want to translate all mentions of $a^{\top}$ to $a$.
\end{itemize}
